---
title: "Symbiodiniaceae community dynamics in *Pocillopora* colonies from Uva Island reef during 2014-2016"
author: "Ana Palacio"
date: "October 7, 2019"
output:
  html_document:
    fig_height: 7
    fig_width: 7
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

This file analyzes the changes in S/H cell ratio (bleaching) in *Pocillopora* sp:
* In 29 colonies sampled in 2014 (Before ENSO), 2015 (during 1st peak of ENSO) and 2016 (during 2nd peak of ENSO)
* These samples were collected at Uva Island, Gulf of Chiriquí, Panama

```{r libraries}
# Libraries    
    library(tidyverse) # install.packages('tidyverse')
    # library(devtools)  # install.packages("devtools")
    # devtools::install_github("jrcunning/steponeR")
    library(steponeR)
    library(scales)
    library(gridExtra)
    library(lme4)
    library(lmerTest)
    library(multcomp)
    library(emmeans)
   
# Default ggplot settings
    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.line = element_line(colour = "black"),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()

```

## 1. Symbiont to host (S/H) cell ratio and *Durusdinium* proportion

Get the raw data for all Pocillopora samples applying R.Cunning steponeR function

1. Get list of plate files to read data
2. Calculate the ratios 
3. Export results

```{r CalculateRatios, include=FALSE}
Pdam.plates <- list.files(path="data", pattern=".csv", full.names=T)
Pdam.plates

Pdam.Out <- steponeR(files=Pdam.plates, target.ratios=c("C.Pdam", "D.Pdam"), 
                     fluor.norm=list(C=3.798, D=0, Pdam=5.416),
                     copy.number=list(C=9, D=1, Pdam=3),
                     ploidy=list(C=1, D=1, Pdam=2),
                     extract=list(C=0.813, D=0.813, Pdam=0.982))

# Target ratio results
Pdam<-Pdam.Out$result
```

Get colony and year information from sample labels

```{r}
# Parse sample names, times, treatments, colonies, plates
    sample.year <- rbind.fill(lapply(strsplit(as.character(Pdam$Sample.Name), split="_"), 
     function(X) data.frame(t(X))))
        colnames(sample.year) <- c("Spp", "Colony","Year")
        Pdam <- cbind(sample.year, Pdam[,-1])

# Keep unique sample ID to check reruns  
    Pdam$Sample<-paste(Pdam$Year,Pdam$Colony, sep="_")
    Pdam$ID<-paste(Pdam$Sample,Pdam$File.Name, sep=".")
```

Calculate total S/H ratio and D/C ratio and propD

```{r, include=FALSE}

# 0. If Clade only detected in one technical replicate, set its ratio to NA (becomes zero)
  Pdam$C.Pdam[which(Pdam$C.reps==1)] <- NA
  Pdam$D.Pdam[which(Pdam$D.reps==1)] <- NA

# 1. Rename cols and make NA=0
  colnames(Pdam)[which(colnames(Pdam) %in% c("C.Pdam", "D.Pdam" ))] <- c("C.SH", "D.SH")  

  Pdam$C.SH[is.na(Pdam$C.SH)] <- 0
  Pdam$D.SH[is.na(Pdam$D.SH)] <- 0
  
  Pdam <- Pdam[, c("Colony", "Year", "C.SH", "D.SH","Sample", "ID")]
  
# 2. Get the ratios and log 10
  # Total ratio
  Pdam$tot.SH <- Pdam$C.SH + Pdam$D.SH  
  Pdam$logTot.SH <- log10(Pdam$tot.SH ) 
  
  # C ratio
  Pdam$logC.SH <- log10(Pdam$C.SH)
    
  # D ratio
  Pdam$logD.SH <- log10(Pdam$D.SH)  
    
  Pdam$logTot.SH[which(Pdam$tot.SH==0)] <- NA
  Pdam$logC.SH[which(Pdam$C.SH==0)] <- NA
  Pdam$logD.SH[which(Pdam$D.SH==0)] <- NA
    
# Clade Proportion
  # D Proportion
  Pdam$D.Prp<-(Pdam$D.SH/Pdam$tot.SH)
  # C Proportion
  #Pdam$C.Prp<-(Pdam$C.SH/Pdam$tot.SH)
  
  hist(Pdam$D.Prp)
  #Dproportion<-Pdam[(Pdam$D.Prp<0.99 & Pdam$D.Prp>0.01),]
  #hist(Dproportion$D.Prp)
```

Most of the colonies are dominated by one symbiont genus

## 2. qPCR DATA CLEANING and quality control

```{r DataCleaning}
 
 ## 1. Check and remove NTC wells
  ntc <- Pdam[which(Pdam$Colony=="NTC"), ]
  Pdam <- droplevels(Pdam[!rownames(Pdam) %in% rownames(ntc), ])
  
  ## 2. Check and remove NoHSratio samples
  NoHSratio <- Pdam[which(Pdam$tot.SH==0), ]
  Pdam <- droplevels(Pdam[!rownames(Pdam) %in% rownames(NoHSratio), ])

  ## 3. Chose bw samples ran more than once
  ReRunA <- Pdam[duplicated(Pdam$Sample),]
  
  n_RunA <- data.frame(table(Pdam$Sample))
  colnames(n_RunA)<-c("Sample","RanA")
  Pdam<-join(Pdam, n_RunA, type = "left")
  
  DuplicatesA <- Pdam[(Pdam$RanA>1),]
  
  # Remove bad replicates
  ToRem1<-read.csv("ToRemove10-28-16.csv")  # 11/1/16
  Pdam<-Pdam[!(Pdam$ID %in% ToRem1$ID),]
    
  n_RunB <- data.frame(table(Pdam$Sample))
  ReRunB <- Pdam[duplicated(Pdam$Sample),]
  colnames(n_RunB)<-c("Sample","RanB")
  Pdam<-join(Pdam, n_RunB, type = "left")
  
  # List of dupplicated samples, should have 0 rows now
  DuplicatesB <- Pdam[(Pdam$RanB>1),]
  
  # 4. Check and remove samples with high SD or late amplification
  StDe1.5 <- Pdam[which(Pdam$Pdam.CT.sd>1.5), ]
  Pdam<-Pdam[!(Pdam$ID %in% StDe1.5$ID),]
# End of qPCR data cleaning
```
 
## 3. Field/sample information

Get collection information and select only samples from Uva Island that were sampled in 2014, 2015 and 2016

```{r SampleInfo}
# 1. Labeling and Factors

  ## Import treatment info from Field file 
  Info<-read.csv("SampleInfo.csv", header=TRUE)

  ## Merge SH ratios and sample info
      Pdam<-join(Pdam, Info, by = "Sample", 
                type = "left", match = "all")
      summary(Pdam)

# 2. Uva Data
      # Write how many years a colony was sampled
      Years <- data.frame(table(Pdam$Colony))
      colnames(Years)<-c("Colony","Times")
      Pdam<-join(Pdam, Years, type = "left")
  # Select data only from Uva Island    
      data.Uva<-Pdam[which(Pdam$Location=="Uva Island"), ]
  # Select colonies that were sampled three times (2014, 2015 and 2016)
      data.Uva<-data.Uva[which(data.Uva$Times>2),]
  # Remove "Ross" samples (colony in deep location (~50feet), not Uva reef) 
  # and 259 as well as 264 that were mislabeled in at least one of the sampling points   
      data.Uva<-filter(data.Uva, Colony!="Ross")
      data.Uva<-filter(data.Uva, Colony!="259-1")
      data.Uva<-filter(data.Uva, Colony!="264-1")

      data.Uva<-data.Uva[,c("Colony","Year.2","C.SH","D.SH","tot.SH",
                            "logTot.SH","D.Prp", "logC.SH", "logD.SH","Year","Sample")]
      data.Uva$Year<-factor(data.Uva$Year, levels=c("14", "15", "16"))
      data.Uva$Colony<-factor(data.Uva$Colony)
    summary(data.Uva)
    
```

## 4. Community classification by genera presence/dominance 

### Symbiodiniaceae genera detected in the samples (Only-C, Only-D, Mixed communities)

```{r}
# Add a column for the genera detected using qPCR
  data.Uva$Community<-NULL
  data.Uva$Community[which(data.Uva$D.Prp>=0)] <- "Mixed"
  data.Uva$Community[which(data.Uva$D.Prp==0)] <- "Cladocopium-only"
  data.Uva$Community[which(data.Uva$D.Prp==1)] <- "Durusdinium-only"

  data.Uva$Community<-factor(as.character(data.Uva$Community), 
                         levels=c("Cladocopium-only", "Mixed", "Durusdinium-only"))
  
# Summary genera detected
  Summary_Community<-data.Uva %>%
        group_by(Year.2, Community) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community

```

### Dominant Symbiodiniaceae genus in each sample (C-dominated, D-dominated)

In general, Pocillipora colonies are dominated by one Symbiodiniaceae type that accounts for more than 90 of the symbiont community. However, sometimes intermediate proportions are common when the symbiont community is transitioning from being dominated by one algal type to other (e.g. during heat stress). 

For this data set, 2 of the colonies sampled in 2014 had relativelly even proportions of *Cladocopium*_b and *Durusdinim glynnii* (Colony 267_2014, D proportion = 0.47; Colony 269_2014, D proportion = 0.50). This made difficult their classification into one domminant type for statistical testing and further plotting. Since these 2 colonies were later dominated by *Durusdinim glynnii* in 2015, we decided to include them in the D-dominated classification, eventhoug in 2014 there were not such a dominance (See figure 2). 

```{r}
 # Add a column for the dominant genus
  data.Uva$DominantCommunity<-NULL
  #data.Uva$Community[which(data.Uva$D.Prp>0.1 & data.Uva$D.Prp<0.50)] <- "CD"
  #data.Uva$Community[which(data.Uva$D.Prp>0.5 & data.Uva$D.Prp<0.9)] <- "DC"
  data.Uva$DominantCommunity[which(data.Uva$D.Prp>=0.45)] <- "Durusdinium-dominated"  
  data.Uva$DominantCommunity[which(data.Uva$D.Prp<0.45)] <- "Cladocopium-dominated"
  
  data.Uva$DominantCommunity<-factor(as.character(data.Uva$DominantCommunity),
                              levels=c("Cladocopium-dominated","Durusdinium-dominated"))
# Summary dominant genera
  Summary_Community2<-data.Uva %>%
        group_by(Year.2, DominantCommunity) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community2
``` 

### Changes in the number of colonies dominated by each genus

To test the statistical significance of changes in the number of colonies dominated by *Durusdinium* versus *Cladocopium* we considered inclussion and exclussion of these 2 initially even colonies, and to place them in the D-dominated or C-dominated categories in 2014.

* Fisher test including initially (Aug 2014) even colonies. Both colonies placed in the D-dominated category.

```{r}
Input =("
Year    C     D
2014    15   14
2016    8    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```


* Fisher test including initially (Aug 2014) even colonies. One colony was placed in the C-dominated category (D proportion=0.47), while the second one was placed in the D-dominated category (D proportion = 0.50)

```{r}
Input =("
Year    C     D
2014    16   13
2016    8    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")
```

* Fisher test removing initially (Aug 2014) even colonies. N=27 colonies instead 29

```{r}
Input =("
Year    C     D
2014    15   12
2016    8    19
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```

* Fisher test including initially (Aug 2014) even colonies. Both colonies placed in the C-dominated category (D proportion=0.47, colony 267; and 0.50, colony 269)

```{r}
Input =("
Year    C     D
2014    17   12
2016    8    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```


---

## 5a. qPCR based analysis (Symbiodiniaceae genera hosted)

Set initial (2014) and final (2016) communities for each sample 

```{r}
  # Subset Aug 2014,  Aug 2015 and April 2016 samples
  D2014.data<-subset(data.Uva, Year.2==2014)
  D2014.data<-D2014.data[,c("Colony","D.Prp","Community","DominantCommunity")]
  colnames(D2014.data)<-(c("Colony","D14.D.Prp","D14Community", "D14Dominant"))
  data.Uva<-left_join(data.Uva, D2014.data, by=c("Colony")) # Add initial community to all samples
   
  # D2015.data<-subset(data.Uva, Year.2==2015)
  # D2015.data<-D2015.data[, c("Colony","D.Prp","Community")]
  # colnames(D2015.data)<-(c("Colony","D15.D.Prp","D15Community"))
  # # data.Uva<-left_join(data.Uva, D2015.data, by=c("Colony"))

  D2016.data<-subset(data.Uva, Year.2==2016) # D1a under control temperature
  D2016.data<-D2016.data[, c("Colony","D.Prp","Community","DominantCommunity")]
  colnames(D2016.data)<-(c("Colony","D16.D.Prp","D16Community", "D16Dominant"))
  data.Uva<-left_join(data.Uva, D2016.data, by=c("Colony")) # Add final community to all samples
  
```


## 6a. Changes in colony proportions based on detected genera (qPCR)

* Based on detected Symbiodiniacea genera in 2014 (qPCR)

```{r}
Histo_Dprop <- ggplot(data.Uva, aes (D.Prp , fill=(D14Community))) + ggthe_bw +
  geom_histogram(binwidth = 0.05, boundary=0) +
  facet_grid(~Year.2, labeller = labeller(Year.2=c(
                `2014` = "August 2014", `2015` = "August 2015", `2016` = "April 2016"))) +
  scale_fill_manual(values=c("blue3","purple", "red3"),
                    guide = guide_legend(title.position = "top", nrow = 1),
                    name = "Initial symbiont community (August 2014)", 
                    labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
    scale_x_continuous(name= expression(
    italic(Durusdinium)~proportion~(D/H)/(S/H)),
                     breaks=(seq(0,1,by=0.1))) +
    scale_y_continuous((name= "Number of colonies"),
                     breaks=seq(0,15,by=5)) +
    theme(legend.position="bottom",
        legend.title.align=0.5,
        strip.background =element_rect(fill=NA))
Histo_Dprop +coord_flip()

```

```{r}
Traject_Proportion_Facet <- ggplot (data.Uva) +
   ggthe_bw + 
    geom_line(aes (x=Year.2, D.Prp, colour=factor(Colony)))+ 
    facet_wrap(~D14Community, labeller = labeller(
    D14Community=c(`Cladocopium-only` = "Cladocopium-only (2014)", 
                   `Mixed` = "Mixed (2014)", 
                   `Durusdinium-only` = "Durusdinium-only (2014)"))) +
    geom_jitter(aes(Year.2, D.Prp, colour=factor(Colony)), alpha=0.3, 
              height = 0.05, width = 0.15) +
    #labs(x = "Año del muestreo", y = "Durusdinium Proportion") +
    theme(legend.position="none")
Traject_Proportion_Facet
```

### Figure 2: qPCR

```{r}
Histo2014_Dprop <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(D14Community))) +
      ggthe_bw + coord_flip()+ ggtitle("a.")+
      geom_histogram(binwidth = 0.05, boundary=0) +
      scale_fill_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Initial symbiont community (August 2014)", 
                        labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
      scale_x_continuous(name= expression(
                        italic(Durusdinium)~proportion~((D/H)/(S/H))),
                        breaks=(seq(0,1,by=0.1)),
                        expand=c(0.01,0.01)) +
      scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                        limits = c(0,17),
                        breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
#Histo2014_Dprop 

Histo2016_Dprop <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(D14Community))) +
      ggthe_bw + coord_flip()+ ggtitle("c.")+
      geom_histogram(binwidth = 0.05, boundary=0) +
      scale_fill_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Initial symbiont community (August 2014)", 
                        labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
      scale_x_continuous(name="",
                        breaks=(seq(0,1,by=0.1)),
                        expand=c(0.01,0.01)) +    
      scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                        limits = c(0,17),
                        breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
#Histo2016_Dprop

Traject_Proportion<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp , colour=(D14Community), group=(Colony))) + ggthe_bw + ggtitle("b.") +
  geom_line(linetype=2) +
  geom_jitter(height = 0.01, width = 0.25, alpha=0.4) +
  
  scale_colour_manual(values=c("blue3","purple", "red3"),
                    guide = guide_legend(title.position = "top", nrow = 1),
                    name = "Initial symbiont community (August 2014)", 
                    labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
  scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
  scale_y_continuous((name= ""),
                     breaks=seq(0,1,by=0.1),
                     expand=c(0.01,0.01)) +
  
  theme(legend.position="bottom",
        legend.title.align=0.5,
        strip.background =element_rect(fill=NA))
#Traject_Proportion

Figure_2<-grid.arrange(Histo2014_Dprop,Traject_Proportion, Histo2016_Dprop,
nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_2qPCR.svg", plot=Figure_2, width=7, height=4)

```

## 7a. Changes in total Symbiodiniaceae abundance (bleaching): qPCR

* Only considering initial (2014) community

```{r}
SH_2014Co<-lmerTest::lmer(logTot.SH ~ Year * D14Community + (1|Colony), data=data.Uva)
    summary(SH_2014Co)
    #step(SH_2014Co)
    
    SH.emmc<-emmeans(SH_2014Co, ~Year*D14Community)
    SH_groups<-multcomp::cld(SH.emmc)
    SH_groups
    
    plot(emmeans(SH_2014Co, ~Year|~D14Community), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~D14Community)
    
    
SH_2014Com <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(D14Community))) +  ggthe_bw +
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1, 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.95)) +
      
      scale_colour_manual(values=c("blue","purple", "red"),
                            guide = guide_legend(title.position = "top", nrow = 1),
                            name = "Symbionts detectec in 2014",
                            labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.5,0.1),
            strip.background =element_rect(fill="white")) +
      scale_y_continuous(limits = c(-3, -0.8),
                name="\n Total symbiont to host cell ratio (S/H)", 
                labels = (math_format(10^.x)),
                expand = c(0.0, 0)) + 
      scale_x_discrete(name="Year")
SH_2014Com
```   

* Only considering current community

```{r}
SH_Community<-lmerTest::lmer(logTot.SH ~ Year * Community + (1|Colony), data=data.Uva)
    summary(SH_Community)
    #step(SH_Community)
    
    SH.emmc<-emmeans(SH_Community, ~Year*Community)
    SH_groups<-multcomp::cld(SH.emmc)    
    #write.csv(SH_groups,"SH_groupsB.csv")
    
plot(emmeans(SH_Community, ~Year|~Community), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~Community)

SH_Com <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(Community))) +  ggthe_bw +
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1, 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.95)) +
      
      scale_colour_manual(values=c("blue","purple", "red"),
                            guide = guide_legend(title.position = "top", nrow = 1),
                            name = "Symbionts detectec in 2014",
                            labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.5,0.1),
            strip.background =element_rect(fill="white")) +
      scale_y_continuous(limits = c(-3, -0.8),
                name="\n Total symbiont to host cell ratio (S/H)", 
                labels = (math_format(10^.x)),
                expand = c(0.0, 0)) + 
      scale_x_discrete(name="Year")
SH_Com

anova(SH_2014Co, SH_Community)

```    

* Plot based on initial and current symbiont community 

### Figure 3: qPCR

```{r LMER_TotalSH}

SH_Communities<-lmerTest::lmer(logTot.SH ~ Year * D14Community * Community + (1|Colony), data=data.Uva)
    summary(SH_Communities)
    #step(SH_Communities)
    
    SH.emmc<-emmeans(SH_Communities, ~Year*D14Community*Community)
    SH_groups<-cld(SH.emmc)
    SH_groups<-as.data.frame(SH_groups[complete.cases(SH_groups),])
    SH_groups<-SH_groups[order(SH_groups$Year,SH_groups$D14Community, SH_groups$Community),]
    SH_groups
    #write.csv(SH_groups,"SH_Communities_multicomp.csv")

SH_Comties <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(Community))) + ggthe_bw+
    
      facet_grid(~D14Community, labeller = labeller(D14Community=c(
                      `Cladocopium-only` = "Cladocopium-only (2014)",
                      `Mixed` = "Mixed (2014)", 
                      `Durusdinium-only` = "Durusdinium-only (2014)"))) +
        
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.2),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.8),
            name="\n Total symbiont to host cell ratio (S/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(14, 15, 16),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) 
SH_Comties

#ggsave(file="Figure_3.svg", plot=SH_Comties, width=6, height=4)

```

## 8a. Changes in *Cladocopium* abundance

```{r LmerC}

CH_Com <- ggplot(data.Uva, aes (Year.2, logC.SH, colour=factor(Community))) + ggthe_bw+ ggtitle("a.")+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.8),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.7),
            name="\n Cladocopium to host cell ratio (C/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" ", " ", " ")) 
#CH_Com

CH_Com2<-CH_Com + facet_grid(~D14Dominant, labeller = labeller(D14Dominant=c(
                   `Cladocopium-dominated` = "Cladocopium- \n dominated (2014)",
                   `Durusdinium-dominated` = "Durusdinium- \n dominated (2014)")))


CH<-lmer(logC.SH ~ Year* Community* D14Dominant + (1|Colony), data=data.Uva)
    summary(CH)
    #step(CH)

    CH.emmc<-emmeans(CH, ~Year*Community* D14Dominant)
    CH_groups<-cld(CH.emmc)
    CH_groups<-as.data.frame(CH_groups[complete.cases(CH_groups),])
    CH_groups<-CH_groups[order(CH_groups$Year,CH_groups$D14Dominant, CH_groups$Community),]
    CH_groups
    #write.csv(CH_groups,"CH_groups.csv")
    ```
   
## 9a. Changes in *Durusdinium* abundance

```{r LmerD}
DH_Com <- ggplot(data.Uva, aes (Year.2, logD.SH, colour=factor(Community))) + 
      ggthe_bw+ ggtitle("b.")+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.2),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-6, -0.7),
            name="\n Durusdinium to host cell ratio (D/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016"))
                           
# DH_Com

DH_Com2<-DH_Com + facet_grid(~D14Dominant, labeller = labeller(D14Dominant=c(
                   `Cladocopium-dominated` = "Cladocopium- \n dominated (2014)",
                   `Durusdinium-dominated` = "Durusdinium- \n dominated (2014)")))


DH_LM<-lmer(logD.SH ~ Year* Community* D14Dominant + (1|Colony), data=data.Uva)
    summary(DH_LM)
    #step(DH_LM)

    DH.emmc<-emmeans(DH_LM, ~Year*Community* D14Dominant)
    DH_groups<-cld(DH.emmc)
    DH_groups<-as.data.frame(DH_groups[complete.cases(DH_groups),])
    DH_groups<-DH_groups[order(DH_groups$Year,DH_groups$D14Dominant, DH_groups$Community),]
    DH_groups
    #write.csv(DH_groups,"DH_groups.csv")
    ```

### Figure 4: qPCR 

```{r}
Figure_4<-grid.arrange(CH_Com2, DH_Com2,nrow=2)

# ggsave(file="Outputs/Figure_4.svg", plot=Figure_4, width=7, height=4)

```


## 5b. DGGE based analysis (Symbiodiniaceae ITS2 type hosted)

Community classification by ITS2 dominant profile in 2014

```{r}
  # Create a data frame with initial (2014) ITS2 profiles and Pocillopora ORF types 

    # Cladocopium dominated
    ITS2_C1d<-data.frame("Colony"=c("256-1", "257-1", "260-1", "262-1", "330-1", "340-1A"), "ITS2_14"="C1d", "ORF"="Type 3")
   
    
    ITS2_C1bc<-data.frame("Colony"=c("265-1", "266-1", "268-1",  "270-1A", "271-1", "285-1","287-1", "336-1A", "339-1A"),
                          "ITS2_14"="C1bc", 
                          "ORF"="Type 1") # 267 and 269 under D1
    
    #ITS2_C1bc<-data.frame("Colony"=c("265-1", "266-1","267", "268-1", "269-1", "270-1A", "271-1", "285-1","287-1", "336-1A", "339-1A"),
    #                    "ITS2_14"="C1bc", 
    #                    "ORF"="Type 1") # 267 and 269 under C1bc
    
    ITS2_C<-rbind(ITS2_C1d, ITS2_C1bc)
    
    # Durusdinium dominated
    ITS2_D<-anti_join(D2014.data, ITS2_C, by="Colony")
    ITS2_D$ITS2_14<-"D1"
    ITS2_D$ORF<-"Type 1"
    ITS2_D<-ITS2_D[, c("Colony", "ITS2_14", "ORF")]
    
    # Merge initial ITS2 profiles and ORF Pocillopora types with qPCR data
    ITS2<-rbind(ITS2_C, ITS2_D)
    data.Uva<-left_join(data.Uva, ITS2, by=c("Colony")) 
```

## 6b. Changes in colony proportions based on ITS2 profiles (2014) and genus dominance

* Based on ITS2 detected symbionts in 2014

```{r}
Histo_Dprop_ITS2 <- ggplot(data.Uva, aes (D.Prp , fill=(ITS2_14)), shape=(D14Community))  + ggthe_bw +
      geom_histogram(binwidth = 0.05, boundary=0) +
      facet_grid(~Year.2, labeller = labeller(Year.2=c(
                    `2014` = "August 2014", `2015` = "August 2015", `2016` = "April 2016"))) +
      scale_fill_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Initial ITS2 community (August 2014)", 
                        labels=c("C1d", "C1b-c", "D1")) +
      scale_x_continuous(name= expression(
                        italic(Durusdinium)~proportion~(D/H)/(S/H)),
                        breaks=(seq(0,1,by=0.1))) +
      scale_y_continuous((name= "Number of colonies"),
                         breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
Histo_Dprop_ITS2 +coord_flip()

Histo_Dprop_ORF <- ggplot(data.Uva, aes (D.Prp , fill=(ORF)), shape=(D14Community))  + ggthe_bw +
      geom_histogram(binwidth = 0.05, boundary=0) +
      facet_grid(~Year.2, labeller = labeller(Year.2=c(
                    `2014` = "August 2014", 
                    `2015` = "August 2015", `2016` = "April 2016"))) +
      scale_fill_manual(values=c("black","gray"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "ORF type", 
                        labels=c("Type 3", "Type 1")) +
      scale_x_continuous(name= expression(
                        italic(Durusdinium)~proportion~(D/H)/(S/H)),
                        breaks=(seq(0,1,by=0.1))) +
      scale_y_continuous((name= "Number of colonies"),
                         breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
Histo_Dprop_ORF +coord_flip()

```

```{r}

Traject_Proportion_FacetITS2 <- ggplot (data.Uva) +
   ggthe_bw + 
    geom_line(aes (x=Year.2, D.Prp, colour=factor(Colony)))+ 
    facet_wrap(~ITS2_14) +
    geom_jitter(aes(Year.2, D.Prp, colour=factor(Colony)), alpha=0.3, 
              height = 0.05, width = 0.15) +
    #labs(x = "Año del muestreo", y = "Durusdinium Proportion") +
    theme(legend.position="none")
Traject_Proportion_FacetITS2

Traject_Proportion_FacetORF <- ggplot (data.Uva) +
   ggthe_bw + 
    geom_line(aes (x=Year.2, D.Prp, colour=factor(Colony)))+ 
    facet_wrap(~ORF) +
    geom_jitter(aes(Year.2, D.Prp, colour=factor(Colony)), alpha=0.3, 
              height = 0.05, width = 0.15) +
    #labs(x = "Año del muestreo", y = "Durusdinium Proportion") +
    theme(legend.position="none")
Traject_Proportion_FacetORF
```

### Figure 2: ITS2

```{r}
Histo2014_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(ITS2_14))) +
        ggthe_bw + coord_flip()+ ggtitle("a.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
        scale_fill_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Initial ITS2 community (August 2014)", 
                          labels=c("C_a", "C_b", "D1")) +
        scale_x_continuous(name= expression(
                          italic(Durusdinium)~proportion~((D/H)/(S/H))),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Histo2014_DpropITS2 

Histo2016_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(ITS2_14))) +
        ggthe_bw + coord_flip()+ ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
        scale_fill_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Initial ITS2 community (August 2014)", 
                          labels=c("C_a", "C_b", "D1")) +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Histo2016_DpropITS2

Traject_ProportionITS2<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp , colour=(ITS2_14), group=(Colony)))+
        ggthe_bw + ggtitle("b.") +
        geom_line(linetype=2) +
        geom_jitter(height = 0.01, width = 0.25, alpha=0.4) +
        
        scale_colour_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Initial ITS2 community (August 2014)", 
                          labels=c("C_a", "C_b", "D1")) +
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.01,0.01)) +
        
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Traject_ProportionITS2


Figure_2_ITS2<-grid.arrange(Histo2014_DpropITS2, Traject_ProportionITS2,Histo2016_DpropITS2,
nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_ITS2.svg", plot=Figure_2_ITS2, width=7, height=4)

```

### Figure 2: ORF

```{r}
Histo2014_DpropORF <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(ORF))) +
        ggthe_bw + coord_flip()+ ggtitle("a.")+
        geom_histogram(binwidth = 0.05, boundary=0, colour="black") +
        scale_fill_manual(values=c("gray","white"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "ORF Type", 
                          labels=c("Type 3", "Type 1")) +
        scale_x_continuous(name= expression(
                          italic(Durusdinium)~proportion~((D/H)/(S/H))),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                          limits = c(0,16),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA),
              panel.border = element_blank(),
              axis.line = element_line(colour = "black"))
#Histo2014_DpropORF 

Histo2016_DpropORF <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(ORF))) +
        ggthe_bw + coord_flip()+ ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0, 
                       colour="black") +
        scale_fill_manual(values=c("gray","white"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "ORF Type", 
                          labels=c("Type 3", "Type 1")) +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,16),
                          breaks=seq(0,15,by=5)) +
          theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA),
              panel.border = element_blank(),
              axis.line = element_line(colour = "black"))
#Histo2016_DpropORF

Traject_ProportionORF_a<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp))+
        ggthe_bw + ggtitle("b.") +
        geom_line(aes(colour=(ORF), group=(Colony)), linetype=2) +
        scale_colour_manual(values=c("gray", "black"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Pocillopopra type", 
                          labels=c("Type 3", "Type 1")) +
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.01,0.01)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
  
  Traject_ProportionORF <- Traject_ProportionORF_a + 
  geom_jitter((aes(fill=factor(ORF))), 
                    height = 0, width = 0.3, color="black", size=2, shape=21) +
        scale_fill_manual(values=c("gray", "white"))

#Traject_ProportionORF




Figure_2_ORF<-grid.arrange(Histo2014_DpropORF, Traject_ProportionORF, Histo2016_DpropORF,
nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_2_ORF.svg",plot=Figure_2_ORF, width=7, height=4, dpi=300)

```

## 7b. Changes in total Symbiodiniaceae abundance (bleaching): qPCR + Initial ITS2

Only considering initial (2014) community

```{r}
SH_2014CoI<-lmerTest::lmer(logTot.SH ~ Year * ITS2_14 + (1|Colony), data=data.Uva)
    summary(SH_2014CoI)
    #step(SH_2014CoI)
    
    SH_I.emmc<-emmeans(SH_2014CoI, ~Year*ITS2_14)
    SH_I_groups<-multcomp::cld(SH_I.emmc)
    SH_I_groups
    SH_I_groups<-as.data.frame(SH_I_groups[complete.cases(SH_I_groups),])
    SH_I_groups<-SH_I_groups[order(SH_I_groups$Year,SH_I_groups$ITS2_14),]
    SH_I_groups
    
    plot(emmeans(SH_2014CoI, ~Year|~ITS2_14), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~ITS2_14)
    
    
SH_2014ComI <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(DominantCommunity))) +  ggthe_bw + facet_wrap(~ITS2_14) +
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar",  
                   position=position_dodge(width=0.95))+
  stat_summary(fun.data = "mean_cl_boot",geom = "point", 
                   position=position_dodge(width=0.95))+
  stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.95)) +
  
  scale_colour_manual(values=c("blue","purple", "red"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Dominant ITS2 in 2014")+
  theme(legend.position=c(0.5,0.1),
        strip.background =element_rect(fill="white")) +
  scale_y_continuous(limits = c(-3, -0.8),
            name="\n Total symbiont to host cell ratio (S/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
  scale_x_discrete(name="Year")
SH_2014ComI
```   

Only considering current community ADD CURRENT ITS2!

```{r}
C

```    

* Plot based on initial and current symbiont community 

### Figure 3: ITS2

```{r LMER_TotalSH_ITS2}

SH_Communities_I<-lmerTest::lmer(logTot.SH ~ Year * ITS2_14 * Community + (1|Colony), data=data.Uva)
    summary(SH_Communities_I)
    #step(SH_Communities_I)
    
    SH_CI.emmc<-emmeans(SH_Communities_I, ~Year*ITS2_14*Community)
    SH_CI_groups<-cld(SH_CI.emmc)
    SH_CI_groups<-as.data.frame(SH_CI_groups[complete.cases(SH_CI_groups),])
    SH_CI_groups<-SH_CI_groups[order(SH_CI_groups$Year,SH_CI_groups$ITS2_14, SH_CI_groups$Community),]
    SH_CI_groups
    #write.csv(SH_groups,"SH_Communities_multicomp.csv")

SH_ITS2_Comunities <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(Community))) + ggthe_bw+
    
      facet_grid(~ITS2_14, labeller = labeller(ITS2_14=c(
                      `C1d` = "C1d (2014)",
                      `C1bc` = "C1bc (2014)", 
                      `D1` = "D1 (2014)"))) +
        
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.2),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.8),
            name="\n Total symbiont to host cell ratio (S/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) 
SH_ITS2_Comunities

#ggsave(file="Figure_3.svg", plot=SH_ITS2_Comunities, width=6, height=4, dpi=300)

```


## 8b. Changes in *Cladocopium* abundance

```{r LmerC_ITS2}

CH_Com <- ggplot(data.Uva, aes (Year.2, logC.SH, colour=factor(Community))) + ggthe_bw+ ggtitle("a.")+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.8),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.7),
            name="\n Cladocopium to host cell ratio (C/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" ", " ", " ")) 
#CH_Com

CH_Com2ITS2<-CH_Com + facet_grid(~ORF)
# CH_Com2ITS2

CH_I<-lmer(logC.SH ~ Year* Community* ITS2_14 + (1|Colony), data=data.Uva)
    summary(CH_I)
    #step(CH_I)

    CH_I.emmc<-emmeans(CH_I, ~Year*Community* ITS2_14)
    CH_I_groups<-cld(CH_I.emmc)
    CH_I_groups<-as.data.frame(CH_I_groups[complete.cases(CH_I_groups),])
    CH_I_groups<-CH_I_groups[order(CH_I_groups$Year,CH_I_groups$ITS2_14, CH_I_groups$Community),]
    CH_I_groups
    #write.csv(CH_I_groups,"CH_I_groups.csv")
    ```
   
## 9b. Changes in *Durusdinium* abundance

```{r LmerD_ITS2}

DH_ComI <- ggplot(data.Uva, aes (Year.2, logD.SH, colour=factor(Community))) + 
      ggthe_bw+ ggtitle("b.")+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.2),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-6, -0.7),
            name="\n Durusdinium to host cell ratio (D/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016"))

DH_Com2ITS2<-DH_ComI + facet_grid(~ORF)
DH_Com2ITS2

DH_LM_ITS2<-lmer(logD.SH ~ Year* Community* ITS2_14 + (1|Colony), data=data.Uva)
    summary(DH_LM_ITS2)
    #step(DH_LM_ITS2)

library(emmeans)
    DH_I.emmc<-emmeans(DH_LM_ITS2, ~Year*Community* ITS2_14)
    DH_groups_I<-cld(DH_I.emmc)
    DH_groups_I<-as.data.frame(DH_groups_I[complete.cases(DH_groups_I),])
    DH_groups_I<-DH_groups_I[order(DH_groups_I$Year,DH_groups_I$ITS2_14, DH_groups_I$Community),]
    DH_groups_I
    #write.csv(DH_groups_I,"DH_I_groups.csv")
    ```

### Figure 4: qPCR 

```{r}
Figure_4b<-grid.arrange(CH_Com2ITS2, DH_Com2ITS2,nrow=2)

# ggsave(file="Outputs/Figure_4b.svg", plot=Figure_4, width=7, height=4)

```


---

## 10. Supplmenmtary C/H D/H dynamics

Select data

```{r}
log_Log.data<-data.Uva[,c("Colony","Year.2", "C.SH", "D.SH", 
                          "D14Community", "Community","ITS2_14")]

log_Log.data<-log_Log.data %>%
  filter(Year.2 != "2015")

log_Log.data$logC<-log10(log_Log.data$C.SH)
log_Log.data$logD<-log10(log_Log.data$D.SH)
log_Log.data$logC[which(log_Log.data$C.SH==0)] <- -6
log_Log.data$logD[which(log_Log.data$D.SH==0)] <- -6

```

Plot Black and White 

```{r}
Community_Changes2 <- ggplot (log_Log.data, aes(logC, logD, gropup=Colony)) +

  geom_abline(intercept=0, slope=1, linetype=1, color="black")+
  geom_abline(intercept=-1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=-2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=-3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-5, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=5, slope=1, linetype=2, color="gray")+
  
  ggthe_bw + 
  scale_x_continuous(limits = c(-6,-0.1), "log10 (C/H cell ratio)")+
  scale_y_continuous(limits = c(-6,-0.1), "log10 (D/H cell ratio)") +
  
  geom_point(alpha=0.5, size=4) +
  geom_path(size = 1,arrow =
              arrow(type = "open", angle = 30, length = unit(0.1, "inches")))+
  
  annotate("text", x = c(seq(-5.1, -1.1, by=1)), y = -0.9, label = c(
    "10,0000C : D", "1,000C : 1D", "100C : 1D","10C : 1D", "C : D"), angle = 45)+
  annotate("text", x = -0.9, y = c(seq(-4.7, -1.7, by=1)), label = c(
    "1C : 10,000D", "1C : 1,000D", "1C : 100D",  "1C : 10D"), angle = 45)
  
Community_Changes2

#ggsave(file="FigAndrewsFavoriteGraph_BW.svg", plot=Community_Changes2, width=5, height=5)

```

```{r}
Community_Changes3 <- ggplot (log_Log.data, aes(logC, logD, gropup=Colony, colour=D14Community)) +

  geom_abline(intercept=0, slope=1, linetype=1, color="black")+
  geom_abline(intercept=-1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=-2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=-3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-5, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=5, slope=1, linetype=2, color="gray")+
  scale_colour_manual(values=c("blue","purple", "red"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts (2014)",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
  
  ggthe_bw + theme(legend.position="bottom")+
  scale_x_continuous(limits = c(-6,-0.1), "log10 (C/H cell ratio)")+
  scale_y_continuous(limits = c(-6,-0.1), "log10 (D/H cell ratio)") +
  
  geom_point(alpha=0.5, size=4) +
  geom_path(size = 1,arrow =
              arrow(type = "open", angle = 30, length = unit(0.1, "inches")))+
  
  annotate("text", x = c(seq(-5.1, -1.1, by=1)), y = -0.9, label = c(
    "10,0000C : D", "1,000C : 1D", "100C : 1D","10C : 1D", "C : D"), angle = 45)+
  annotate("text", x = -0.9, y = c(seq(-4.7, -1.7, by=1)), label = c(
    "1C : 10,000D", "1C : 1,000D", "1C : 100D",  "1C : 10D"), angle = 45)
  
Community_Changes3

# ggsave(file="FigAndrewsFavoriteGraph_qPCR.svg", plot=Community_Changes3, width=6, height=6)

```

```{r}

Community_Changes4 <- ggplot (log_Log.data, aes(logC, logD, gropup=Colony, colour=ITS2_14)) +

  geom_abline(intercept=0, slope=1, linetype=1, color="black")+
  geom_abline(intercept=-1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=-2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=-3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-5, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=5, slope=1, linetype=2, color="gray")+
  scale_colour_manual(values=c("blue","purple", "red"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Main ITS2 types (2014)",
                        labels=c("C_a", "C_b", "D1"))+
  
  ggthe_bw + theme(legend.position="bottom", 
                    legend.box = "horizontal")+
  scale_x_continuous(limits = c(-6,-0.1), "log10 (C/H cell ratio)")+
  scale_y_continuous(limits = c(-6,-0.1), "log10 (D/H cell ratio)") +
  
  geom_point(alpha=0.5, size=4) +
  geom_path(size = 1,arrow =
              arrow(type = "open", angle = 30, length = unit(0.1, "inches")))+
  
  annotate("text", x = c(seq(-5.1, -1.1, by=1)), y = -0.9, label = c(
    "10,0000C : D", "1,000C : 1D", "100C : 1D","10C : 1D", "C : D"), angle = 45)+
  annotate("text", x = -0.9, y = c(seq(-4.7, -1.7, by=1)), label = c(
    "1C : 10,000D", "1C : 1,000D", "1C : 100D",  "1C : 10D"), angle = 45)
  
Community_Changes4

#ggsave(file="FigAndrewsFavoriteGraph_ITS2.svg", plot=Community_Changes4, width=6, height=6)
``` 
