---
title: "Symbiodiniaceae community dynamics in *Pocillopora* colonies from Uva Island reef during 2014-2016"
author: "Ana Palacio-Castro"
date: "March 29, 2020"
output:
  html_document:
    fig_height: 7
    fig_width: 7
    df_print: paged
    toc: yes
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

This file analyzes the changes in S/H cell ratio (bleaching and symbiont shuffling) in *Pocillopora* spp.:
* 29 colonies were sampled in 2014 (Before ENSO), 2015 (during a 1st peak of heat) and 2016 (after a 2nd peak of heat)
* These samples were collected at Uva Island, Gulf of Chiriquí, Panama.

```{r libraries}
# Libraries    
    library(plyr)
    library(tidyverse) # install.packages('tidyverse')
    # library(devtools)  # install.packages("devtools")
    # devtools::install_github("jrcunning/steponeR")
    library(steponeR)
    library(scales)
    library(gridExtra)
    library(lme4)
    library(lmerTest)
    library(multcomp)
    library(emmeans)
   
# Default ggplot settings
    ggthe_bw<-theme_bw() +
      theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.line = element_line(colour = "black"),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )

```

## 1. Symbiont to host (S/H) cell ratio and *Durusdinium* proportion

Get the raw data for all *Pocillopora* samples applying R.Cunning steponeR function

* Get list of plate files to read data
* Calculate the ratios 
* Export results

```{r CalculateRatios}
Pdam.plates <- list.files(path="data", pattern=".csv", full.names=T)
Pdam.plates

Pdam.Out <- steponeR(files=Pdam.plates, target.ratios=c("C.Pdam", "D.Pdam"), 
                     fluor.norm=list(C=3.798, D=0, Pdam=5.416),
                     copy.number=list(C=9, D=1, Pdam=3),
                     ploidy=list(C=1, D=1, Pdam=2),
                     extract=list(C=0.813, D=0.813, Pdam=0.982))

# Target ratio results
Pdam<-Pdam.Out$result
```

Get colony and year information from sample labels

```{r}
# Parse sample names, times, treatments, colonies, plates
    sample.year <- rbind.fill(lapply(strsplit(as.character(Pdam$Sample.Name), split="_"), 
     function(X) data.frame(t(X))))
        colnames(sample.year) <- c("Spp", "Colony","Year")
        Pdam <- cbind(sample.year, Pdam[,-1])

# Keep unique sample ID to check reruns  
    Pdam$Sample<-paste(Pdam$Year,Pdam$Colony, sep="_")
    Pdam$ID<-paste(Pdam$Sample,Pdam$File.Name, sep=".")
```

Calculate total S/H ratio and D/C ratio and Proportion of *Durusdinium* in each sample

```{r}

# 0. If Clade only detected in one technical replicate, set its ratio to NA (becomes zero)
  Pdam$C.Pdam[which(Pdam$C.reps==1)] <- NA
  Pdam$D.Pdam[which(Pdam$D.reps==1)] <- NA

# 1. Rename cols and make NA=0
  colnames(Pdam)[which(colnames(Pdam) %in% c("C.Pdam", "D.Pdam" ))] <- c("C.SH", "D.SH")  

  Pdam$C.SH[is.na(Pdam$C.SH)] <- 0
  Pdam$D.SH[is.na(Pdam$D.SH)] <- 0
  
  Pdam <- Pdam[, c("Colony", "Year", "C.SH", "D.SH","Sample", "ID")]
  
# 2. Get the ratios and log 10
  # Total ratio
  Pdam$tot.SH <- Pdam$C.SH + Pdam$D.SH  
  Pdam$logTot.SH <- log10(Pdam$tot.SH ) 
  
  # C ratio
  Pdam$logC.SH <- log10(Pdam$C.SH)
    
  # D ratio
  Pdam$logD.SH <- log10(Pdam$D.SH)  
    
  Pdam$logTot.SH[which(Pdam$tot.SH==0)] <- NA
  Pdam$logC.SH[which(Pdam$C.SH==0)] <- NA
  Pdam$logD.SH[which(Pdam$D.SH==0)] <- NA
    
# Clade Proportion
  # D Proportion
  Pdam$D.Prp<-(Pdam$D.SH/Pdam$tot.SH)
  # C Proportion
  #Pdam$C.Prp<-(Pdam$C.SH/Pdam$tot.SH)
  
  hist(Pdam$D.Prp)
  #Dproportion<-Pdam[(Pdam$D.Prp<0.99 & Pdam$D.Prp>0.01),]
  #hist(Dproportion$D.Prp)
```

**Note**: Most of the colonies are dominated by one symbiont genus. Even proportions of multiple symbionts are rare.

## 2. qPCR Data Cleaning and quality control

```{r DataCleaning}
 
 ## 1. Check and remove NTC wells
  ntc <- Pdam[which(Pdam$Colony=="NTC"), ]
  Pdam <- droplevels(Pdam[!rownames(Pdam) %in% rownames(ntc), ])
  
  ## 2. Check and remove NoHSratio samples
  NoHSratio <- Pdam[which(Pdam$tot.SH==0), ]
  Pdam <- droplevels(Pdam[!rownames(Pdam) %in% rownames(NoHSratio), ])

  ## 3. Chose bw samples ran more than once
  ReRunA <- Pdam[duplicated(Pdam$Sample),]
  
  n_RunA <- data.frame(table(Pdam$Sample))
  colnames(n_RunA)<-c("Sample","RanA")
  Pdam<-join(Pdam, n_RunA, type = "left")
  
  DuplicatesA <- Pdam[(Pdam$RanA>1),]
  
  # Remove bad replicates
  ToRem1<-read.csv("ToRemove10-28-16.csv")  # 11/1/16
  Pdam<-Pdam[!(Pdam$ID %in% ToRem1$ID),]
    
  n_RunB <- data.frame(table(Pdam$Sample))
  ReRunB <- Pdam[duplicated(Pdam$Sample),]
  colnames(n_RunB)<-c("Sample","RanB")
  Pdam<-join(Pdam, n_RunB, type = "left")
  
  # List of duplicated samples, should have 0 rows now
  DuplicatesB <- Pdam[(Pdam$RanB>1),]
  
  # 4. Check and remove samples with high SD or late amplification
  StDe1.5 <- Pdam[which(Pdam$Pdam.CT.sd>1.5), ]
  Pdam<-Pdam[!(Pdam$ID %in% StDe1.5$ID),]
# End of qPCR data cleaning
```
 
## 3. Field/sample information

Get collection information and select only samples from Uva Island that were sampled in 2014, 2015 and 2016

```{r SampleInfo}
# 1. Labeling and Factors

  ## Import treatment info from Field file and mortality / ITS2 / ORF data
  Info<-read.csv("SampleInfo.csv", header=TRUE)
  Mortality<-read.csv("MortalityData.csv", header=TRUE)
  Mortality$ITS_2<-factor(Mortality$ITS_2, level=c("C1d", "C1b-c", "D1"))


  ## Merge SH ratios and sample info
      Pdam<-join(Pdam, Info, by = "Sample", 
                type = "left", match = "all")
      #summary(Pdam)

# 2. Uva Data
      # Write how many years a colony was sampled
      Years <- data.frame(table(Pdam$Colony))
      colnames(Years)<-c("Colony","Times")
      Pdam<-join(Pdam, Years, type = "left")
  # Select data only from Uva Island    
      data.Uva<-Pdam[which(Pdam$Location=="Uva Island"), ]
  # Select colonies that were sampled three times (2014, 2015 and 2016)
      data.Uva<-data.Uva[which(data.Uva$Times>2),]
  # Remove "Ross" samples (colony in deep location (~50feet), not Uva reef) 
  # and 259 as well as 264 that were mislabeled in at least one of the sampling points   
      data.Uva<-filter(data.Uva, Colony!="Ross")
      data.Uva<-filter(data.Uva, Colony!="259-1")
      data.Uva<-filter(data.Uva, Colony!="264-1")

      data.Uva<-data.Uva[,c("Colony","Year.2","C.SH","D.SH","tot.SH",
                            "logTot.SH","D.Prp", "logC.SH", "logD.SH",
                            "Year","Sample", "Reef", "Spp", "Depht")]
      data.Uva$Year<-factor(data.Uva$Year, levels=c("14", "15", "16"))
      data.Uva$Colony<-factor(data.Uva$Colony)
      
    #summary(data.Uva)
    
  #3. Merge SH ratios and mortality info
      data.Uva<-join(data.Uva, Mortality, by = "Sample", 
                type = "left", match = "all")
      summary(data.Uva)
      
      data.Uva$Mortality<-factor(data.Uva$Mortality, levels =
                              c("No", "Partial", "Almost total"))
      
```

### ORF types versus morphological ID

```{r}
  # Summary ID  *Pocillopora* by Glynn
  Summary_ID_Glynn<-data.Uva %>%
        group_by(Year.2, ORF, ID_Glynn) %>%
        dplyr::summarise(total.count=n()) 
  Summary_ID_Glynn
    
  
  # Summary ID  *Pocillopora* by Palacio
  Summary_ID_Glynn<-data.Uva %>%
        group_by(Year.2, ORF, ID_Palacio) %>%
        dplyr::summarise(total.count=n()) 
  Summary_ID_Glynn  
```

## 4. Community classification by genera presence/dominance 

### Symbiodiniaceae genera detected in the samples (Only-C, Only-D, Mixed communities)

```{r}
# Add a column for the genera detected in each sample using qPCR
  data.Uva$Community<-NULL
  data.Uva$Community[which(data.Uva$D.Prp>=0)] <- "Mixed"
  data.Uva$Community[which(data.Uva$D.Prp==0)] <- "Cladocopium-only"
  data.Uva$Community[which(data.Uva$D.Prp==1)] <- "Durusdinium-only"

  data.Uva$Community<-factor(as.character(data.Uva$Community), 
                         levels=c("Cladocopium-only", "Mixed", "Durusdinium-only"))
  
# Summary genera *Pocillopora*
  Summary_Community<-data.Uva %>%
        group_by(Year.2, Community) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community
  
  # Summary genera detected by ORF type
  Summary_Community<-data.Uva %>%
        group_by(ORF, Year.2, Community) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community

```

### Dominant Symbiodiniaceae genus in each sample (C-dominated, D-dominated)

In general, *Pocillopora* colonies are dominated by one Symbiodiniaceae type that accounts for more than 80-90 of the symbiont community. However, sometimes intermediate proportions are common when the symbiont community is transitioning from being dominated by one algal type to another (e.g. during heat stress). 

For this data set, 2 of the colonies sampled in 2014 had relatively even proportions of *Cladocopium*_C1bc and *Durusdinium glynnii* (Colony 267_2014, D proportion = 0.47; Colony 269_2014, D proportion = 0.50). This made difficult their classification into one dominant type for statistical testing and further plotting. Since these 2 colonies were later dominated by *Durusdinim glynnii* in 2015, we decided to include them in the D-dominated classification, even though in 2014 there was not such a dominance (See figure 3b). 

```{r}
 # Add a column for the dominant genus
  data.Uva$DominantCommunity<-NULL
  data.Uva$DominantCommunity[which(data.Uva$D.Prp>=0.45)] <- "Durusdinium-dominated"  
  data.Uva$DominantCommunity[which(data.Uva$D.Prp<0.45)] <- "Cladocopium-dominated"
  
  data.Uva$DominantCommunity<-factor(as.character(data.Uva$DominantCommunity),
                              levels=c("Cladocopium-dominated","Durusdinium-dominated"))

  # Summary dominant genera *Pocillopora*
  Summary_Community2<-data.Uva %>%
        group_by(Year.2, DominantCommunity) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community2
  
  # Summary dominant genera by ORF type
  Summary_Community3<-data.Uva %>%
        group_by(ORF, Year.2, DominantCommunity) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community3
``` 

Set initial (2014) and final (2016) communities for each colony 

```{r}

  data.Uva$ITS_2<-factor(data.Uva$ITS_2, level=c("C1b-c", "C1d", "D1"))
  # Sub set Aug 2014,  Aug 2015 and April 2016 samples
  D2014.data<-subset(data.Uva, Year.2==2014)
  D2014.data<-D2014.data[,c("Colony","D.Prp","Community","DominantCommunity", "ITS_2")]
  colnames(D2014.data)<-(c("Colony","D14.D.Prp","D14Community", "D14Dominant", "ITS2_14"))
  data.Uva<-left_join(data.Uva, D2014.data, by=c("Colony")) # Add initial community to all samples
   
  D2016.data<-subset(data.Uva, Year.2==2016) # D1a under control temperature
  D2016.data<-D2016.data[, c("Colony","D.Prp","Community","DominantCommunity", "ITS_2")]
  colnames(D2016.data)<-(c("Colony","D16.D.Prp","D16Community", "D16Dominant",  "ITS2_16"))
  data.Uva<-left_join(data.Uva, D2016.data, by=c("Colony")) # Add final community to all samples
  
```

---

# A. Initial qPCR BASED analysis (No ITS2 or ORF information included)... 

Skip to 5b for complete paper results. Section A was my mental process to analyze the symbiont data that got refined once we got the ITS2 and ORF results (B)

## 5a. Changes in the number of *Pocillopora* colonies dominated by each genus

To test the statistical significance of changes in the number of colonies dominated by *Durusdinium* versus *Cladocopium* we considered inclusion and exclusion of these 2 initially even colonies, and to place them in the D-dominated or C-dominated categories in 2014.

* Fisher test including initially (Aug 2014) even colonies. Both colonies were placed in the D-dominated category. P-value= 0.1064

```{r}
Input =("
Year    C     D
2014    15   14
2016    8    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```


* Fisher test including initially (Aug 2014) even colonies. One colony was placed in the C-dominated category (D proportion=0.47), while the second one was placed in the D-dominated category (D proportion = 0.50). P-value = 0.06099

```{r}
Input =("
Year    C     D
2014    16   13
2016    8    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")
```

* Fisher test removing initially (Aug 2014) even colonies. N=27 colonies instead 29. P-value = 0.09778

```{r}
Input =("
Year    C     D
2014    15   12
2016    8    19
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```

* Fisher test including initially (Aug 2014) even colonies. Both colonies placed in the C-dominated category (D proportion=0.47, colony 267; and 0.50, colony 269). p-value = 0.03295

```{r}
Input =("
Year    C     D
2014    17   12
2016    8    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```

## 6a. Changes in colony proportions based on detected genera (qPCR)

* Based on detected Symbiodiniaceae genera in 2014 (qPCR)

```{r}
Histo_Dprop <- ggplot(data.Uva, aes (D.Prp , fill=(D14Community))) + ggthe_bw +
  geom_histogram(binwidth = 0.05, boundary=0) +
  facet_grid(~Year.2, labeller = labeller(Year.2=c(
                `2014` = "August 2014", `2015` = "August 2015", `2016` = "April 2016"))) +
  scale_fill_manual(values=c("blue3","purple", "red3"),
                    guide = guide_legend(title.position = "top", nrow = 1),
                    name = "Initial symbiont community (August 2014)", 
                    labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
    scale_x_continuous(name= expression(
    italic(Durusdinium)~proportion~(D/H)/(S/H)),
                     breaks=(seq(0,1,by=0.1))) +
    scale_y_continuous((name= "Number of colonies"),
                     breaks=seq(0,15,by=5)) +
    theme(legend.position="bottom",
        legend.title.align=0.5,
        strip.background =element_rect(fill=NA))
Histo_Dprop

```

```{r}
Traject_Proportion_Facet <- ggplot (data.Uva) +
   ggthe_bw + 
    geom_line(aes (x=Year.2, D.Prp, colour=factor(Colony)))+ 
    facet_wrap(~D14Community, labeller = labeller(
    D14Community=c(`Cladocopium-only` = "Cladocopium-only (2014)", 
                   `Mixed` = "Mixed (2014)", 
                   `Durusdinium-only` = "Durusdinium-only (2014)"))) +
    geom_jitter(aes(Year.2, D.Prp, colour=factor(Colony)), alpha=0.3, 
              height = 0.05, width = 0.15) +
    #labs(x = "Año del muestreo", y = "Durusdinium Proportion") +
    theme(legend.position="none")
Traject_Proportion_Facet
```

### Figure Not used: qPCR and colony proportion by dominant community

```{r, fig.width=8, fig.height=4}
Histo2014_Dprop <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(D14Community))) +
      ggthe_bw + coord_flip()+ ggtitle("a.")+
      geom_histogram(binwidth = 0.05, boundary=0) +
      scale_fill_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Initial symbiont community (August 2014)", 
                        labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
      scale_x_continuous(name= expression(
                        italic(Durusdinium)~proportion~((D/H)/(S/H))),
                        breaks=(seq(0,1,by=0.1)),
                        expand=c(0.01,0.01)) +
      scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                        limits = c(0,17),
                        breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
#Histo2014_Dprop 

Histo2016_Dprop <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(D14Community))) +
      ggthe_bw + coord_flip()+ ggtitle("c.")+
      geom_histogram(binwidth = 0.05, boundary=0) +
      scale_fill_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Initial symbiont community (August 2014)", 
                        labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
      scale_x_continuous(name="",
                        breaks=(seq(0,1,by=0.1)),
                        expand=c(0.01,0.01)) +    
      scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                        limits = c(0,17),
                        breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
#Histo2016_Dprop

Traject_Proportion<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp , colour=(D14Community), group=(Colony))) + ggthe_bw + ggtitle("b.") +
  geom_line(linetype=2) +
  geom_jitter(height = 0.01, width = 0.25, alpha=0.4) +
  
  scale_colour_manual(values=c("blue3","purple", "red3"),
                    guide = guide_legend(title.position = "top", nrow = 1),
                    name = "Initial symbiont community (August 2014)", 
                    labels=c("Cladocopium-only", "Mixed", "Durusdinium-only")) +
  scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
  scale_y_continuous((name= ""),
                     breaks=seq(0,1,by=0.1),
                     expand=c(0.01,0.01)) +
  
  theme(legend.position="bottom",
        legend.title.align=0.5,
        strip.background =element_rect(fill=NA))
#Traject_Proportion

Figure_2<-grid.arrange(Histo2014_Dprop,Traject_Proportion, Histo2016_Dprop,
nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_2qPCR.svg", plot=Figure_2, width=7, height=4)

```

## 7a. Changes in total Symbiodiniaceae abundance (bleaching): qPCR

### Based on initial (2014) community

```{r}
SH_2014Co<-lmerTest::lmer(logTot.SH ~ Year * D14Community + (1|Colony), data=data.Uva)
    summary(SH_2014Co)
    #step(SH_2014Co)
    
    SH.emmc<-emmeans(SH_2014Co, ~Year*D14Community)
    SH_groups<-multcomp::cld(SH.emmc)
    SH_groups<-SH_groups[order(
                SH_groups$Year, SH_groups$D14Community),]
    SH_groups
    
    plot(emmeans(SH_2014Co, ~Year|~D14Community), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~D14Community)
    
    
SH_2014Com <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(D14Community))) +  ggthe_bw +
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1, 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.95)) +
      
      scale_colour_manual(values=c("blue","purple", "red"),
                            guide = guide_legend(title.position = "top", nrow = 1),
                            name = "Symbionts detected in 2014",
                            labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.5,0.1),
            strip.background =element_rect(fill="white")) +
      scale_y_continuous(limits = c(-3, -0.8),
                name="\n Total symbiont to host cell ratio (S/H)", 
                labels = (math_format(10^.x)),
                expand = c(0.0, 0)) + 
      scale_x_discrete(name="Year")
SH_2014Com
```   

### Based on current community

```{r}
SH_Community<-lmerTest::lmer(logTot.SH ~ Year * Community + (1|Colony), data=data.Uva)
    summary(SH_Community)
    #step(SH_Community)
    
    SH.emmc<-emmeans(SH_Community, ~Year*Community)
    SH_groups<-multcomp::cld(SH.emmc) 
    SH_groups<-SH_groups[order(
                SH_groups$Year, SH_groups$Community),]
    SH_groups
    #write.csv(SH_groups,"SH_groupsB.csv")
    
plot(emmeans(SH_Community, ~Year|~Community), comparisons = TRUE) +
      coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~Community)

SH_Com <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(Community))) +  ggthe_bw +
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 1, 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", 
                       position=position_dodge(width=0.95))+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.95)) +
      
      scale_colour_manual(values=c("blue","purple", "red"),
                            guide = guide_legend(title.position = "top", nrow = 1),
                            name = "Symbionts detected in 2014",
                            labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.5,0.1),
            strip.background =element_rect(fill="white")) +
      scale_y_continuous(limits = c(-3, -0.8),
                name="\n Total symbiont to host cell ratio (S/H)", 
                labels = (math_format(10^.x)),
                expand = c(0.0, 0)) + 
      scale_x_discrete(name="Year")
SH_Com

anova(SH_2014Co, SH_Community)

```    

### Considering initial and current symbiont community: Figure 3: qPCR

```{r LMER_TotalSH}

SH_Communities<-lmerTest::lmer(logTot.SH ~ Year * D14Community * Community + (1|Colony), data=data.Uva)
    summary(SH_Communities)
    #step(SH_Communities)
    
    SH.emmc<-emmeans(SH_Communities, ~Year*D14Community*Community)
    SH_groups<-cld(SH.emmc)
    SH_groups<-as.data.frame(SH_groups[complete.cases(SH_groups),])
    SH_groups<-SH_groups[order(SH_groups$Year,
                               SH_groups$D14Community,
                               SH_groups$Community),]
    SH_groups
    #write.csv(SH_groups,"SH_Communities_multicomp.csv")

SH_Comties <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(Community))) + ggthe_bw+
    
      facet_grid(~D14Community, labeller = labeller(D14Community=c(
                      `Cladocopium-only` = "Cladocopium-only (2014)",
                      `Mixed` = "Mixed (2014)", 
                      `Durusdinium-only` = "Durusdinium-only (2014)"))) +
        
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.2),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.8),
            name="\n Total symbiont to host cell ratio (S/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(14, 15, 16),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) 
SH_Comties

#ggsave(file="Figure_3.svg", plot=SH_Comties, width=6, height=4)

```

## 8a. Changes in *Cladocopium* abundance

```{r LmerC}

CH_Com <- ggplot(data.Uva, aes (Year.2, logC.SH, colour=factor(DominantCommunity))) + ggthe_bw+ ggtitle("a.")+
  #geom_point()+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3","purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Cladocopium", "Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.8),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.7),
            name="\n Cladocopium to host cell ratio (C/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" ", " ", " ")) 
#CH_Com

CH_Com2<-CH_Com + facet_grid(~D14Dominant, labeller = labeller(D14Dominant=c(
                   `Cladocopium-dominated` = "Cladocopium- \n dominated (2014)",
                   `Durusdinium-dominated` = "Durusdinium- \n dominated (2014)")))


CH<-lmer(logC.SH ~ Year* Community* D14Dominant + (1|Colony), data=data.Uva)
    summary(CH)
    #step(CH)

    CH.emmc<-emmeans(CH, ~Year*Community* D14Dominant)
    CH_groups<-cld(CH.emmc)
    CH_groups<-as.data.frame(CH_groups[complete.cases(CH_groups),])
    CH_groups<-CH_groups[order(CH_groups$Year,CH_groups$D14Dominant, CH_groups$Community),]
    CH_groups
    #write.csv(CH_groups,"CH_groups.csv")
    ```
   
## 9a. Changes in *Durusdinium* abundance

```{r LmerD}
DH_Com <- ggplot(data.Uva, aes (Year.2, logD.SH, colour=factor(Community))) + 
      ggthe_bw+ ggtitle("b.")+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3), alpha=0.5)+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Detected symbionts",
                        labels=c("Mixed", "Durusdinium"))+
      theme(legend.position=c(0.82,0.2),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-6, -0.7),
            name="\n Durusdinium to host cell ratio (D/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016"))
                           
# DH_Com

DH_Com2<-DH_Com + facet_grid(~D14Dominant, labeller = labeller(D14Dominant=c(
                   `Cladocopium-dominated` = "Cladocopium- \n dominated (2014)",
                   `Durusdinium-dominated` = "Durusdinium- \n dominated (2014)")))


DH_LM<-lmer(logD.SH ~ Year* Community* D14Dominant + (1|Colony), data=data.Uva)
    summary(DH_LM)
    #step(DH_LM)

    DH.emmc<-emmeans(DH_LM, ~Year*Community* D14Dominant)
    DH_groups<-cld(DH.emmc)
    DH_groups<-as.data.frame(DH_groups[complete.cases(DH_groups),])
    DH_groups<-DH_groups[order(DH_groups$Year,DH_groups$D14Dominant, DH_groups$Community),]
    DH_groups
    #write.csv(DH_groups,"DH_groups.csv")
    ```

### Figure 4: Changes in C/H and D/H  

```{r, fig.width=8, fig.height=10}
Figure_4<-grid.arrange(CH_Com2, DH_Com2,nrow=2)

# ggsave(file="Outputs/Figure_4.svg", plot=Figure_4, width=7, height=4)

```

---------------------

# Symbiodiniaceae ITS2 type + ORF lineage data analysis 

### Added Pocillopora ORF lineage and Symbiodiniaceae ITS2 type hosted in 2014

```{r}

  #data.Uva$Counts<-paste(data.Uva$DominantCommunity, data.Uva$ORFCommunity, sep = "_")
  data.Uva$ORFCommunity<-paste(data.Uva$ORF, data.Uva$Community, sep = "_")
  
  data.Uva$ORFCommunity<-factor(data.Uva$ORFCommunity,
                                levels = c("Type_3_Cladocopium-only", 
                                           "Type_1_Cladocopium-only",
                                           "Type_1_Mixed", 
                                           "Type-1_Durusdinium-only"))
  
  data.Uva$ORFCommunity2<-paste(data.Uva$ORF,
                              data.Uva$DominantCommunity, sep = "_")
  data.Uva$ORFCommunity2<-as.factor(data.Uva$ORFCommunity2)
 
  data.Uva$DominantITS2[which(
    (data.Uva$DominantCommunity=="Durusdinium-dominated") &
    (data.Uva$ORF=="Type_1")
      )] <- "D1-dominated"
  
  data.Uva$DominantITS2[which(
    (data.Uva$DominantCommunity=="Cladocopium-dominated") &
    (data.Uva$ORF=="Type_1")
      )] <- "C1bc-dominated"
  
    data.Uva$DominantITS2[which(
    (data.Uva$DominantCommunity=="Cladocopium-dominated") &
    (data.Uva$ORF=="Type_3")
      )] <- "C1d-dominated"
  
   data.Uva$DominantITS2<-as.factor(data.Uva$DominantITS2)
   
  Summary_Community4<-data.Uva %>%
        group_by(Year.2, DominantITS2) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community4 
   
  Summary_Community5<-data.Uva %>%
        group_by(ORF, Year.2, DominantITS2) %>%
        dplyr::summarise(total.count=n()) 
  Summary_Community5

```

## 5b. Changes in the number of colonies dominated by each genus

* Fisher test including initially (Aug 2014) 50/50 colonies. Both colonies placed in the D-dominated category to be conservative.

```{r}
# Only type 1 colonies (n=23), p-value = 0.03514

Input =("
Year    C     D
2014    9    14
2016    2    21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")


# Type 1 and type 3 colonies: p-value = 0.1064

Input =("
Year    C     D
2014    15    14
2016    8     21
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```


## 6b. Changes in colony proportions based on ITS2 profiles (2014) and genus dominance

* Histograms based on ITS2 detected symbionts in 2014

```{r}
data.Uva$ITS2_14<-factor(data.Uva$ITS2_14, levels = c("C1d", "C1b-c", "D1"))
data.Uva$ITS2_16<-factor(data.Uva$ITS2_16, levels = c("C1d", "C1b-c", "D1"))

Histo_Dprop_ITS2 <- ggplot(data.Uva, aes (D.Prp , fill=(ITS2_14)), shape=(D14Community))  + ggthe_bw +
      geom_histogram(binwidth = 0.05, boundary=0) +
      facet_grid(~Year.2, labeller = labeller(Year.2=c(
                    `2014` = "August 2014", `2015` = "August 2015", `2016` = "April 2016"))) +
      scale_fill_manual(values=c("blue3", "purple", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "Initial ITS2 community (August 2014)", 
                        labels=c("Type 3 + C1d", "Type 1 + C1b-c", "Type 1 + D1")) +
      scale_x_continuous(name= expression(
                        italic(Durusdinium)~proportion~(D/H)/(S/H)),
                        breaks=(seq(0,1,by=0.1))) +
      scale_y_continuous((name= "Number of colonies"),
                         breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
Histo_Dprop_ITS2 +coord_flip()

```

* Histograms based on ORF lineage

```{r}

Histo_Dprop_ORF <- ggplot(data.Uva, aes (D.Prp , fill=(ORF)), shape=(D14Community))  + ggthe_bw +
      geom_histogram(binwidth = 0.05, boundary=0) +
      facet_grid(~Year.2, labeller = labeller(Year.2=c(
                    `2014` = "August 2014", 
                    `2015` = "August 2015", `2016` = "April 2016"))) +
      scale_fill_manual(values=c("black","gray"),
                        guide = guide_legend(title.position = "top", nrow = 1),
                        name = "ORF type", 
                        labels=c("Type 3", "Type 1")) +
      scale_x_continuous(name= expression(
                        italic(Durusdinium)~proportion~(D/H)/(S/H)),
                        breaks=(seq(0,1,by=0.1))) +
      scale_y_continuous((name= "Number of colonies"),
                         breaks=seq(0,15,by=5)) +
      theme(legend.position="bottom",
            legend.title.align=0.5,
            strip.background =element_rect(fill=NA))
Histo_Dprop_ORF +coord_flip()

```

* Durusdinium proportion trajectory 

```{r}

# By ITS2 type
Traject_Proportion_FacetITS2 <- ggplot (data.Uva) +
   ggthe_bw + 
    geom_line(aes (x=Year.2, D.Prp, colour=factor(Colony)))+ 
    facet_wrap(~ITS2_14) +
    geom_jitter(aes(Year.2, D.Prp, colour=factor(Colony)), alpha=0.3, 
              height = 0.05, width = 0.15) +
    #labs(x = "Año del muestreo", y = "Durusdinium Proportion") +
    theme(legend.position="none")
Traject_Proportion_FacetITS2

# By Depth
Traject_Proportion_FacetORF <- ggplot (data.Uva) +    ggthe_bw +
      geom_line(aes (x=Year.2, D.Prp, group=Colony, linetype=(ORF)))+
      geom_jitter(aes(Year.2, D.Prp, colour=(Depht), shape=ORF),
              height = 0.00, width = 0.25, size=3, alpha=0.7) +  
      scale_colour_gradient(low = "red", high = "blue")
Traject_Proportion_FacetORF

```

!### Figure XX: ITS2

```{r}
Histo2014_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(ITS2_14))) +
        ggthe_bw + ggtitle("a.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
        scale_fill_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Dominant ITS2 community (August 2014)", 
                          labels=c("C1d", "C1b-c", "D.glynnii")) +
        scale_x_continuous(name= expression(
                          italic(Durusdinium)~proportion),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Histo2014_DpropITS2 

Histo2016_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(ITS2_16))) +
        ggthe_bw + ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
        scale_fill_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Dominant ITS2 community (April 2016)", 
                          labels=c("C1d", "C1b-c", "D.glynnii")) +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Histo2016_DpropITS2

Traject_ProportionITS2<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp , 
                                fill=ITS2_14, shape=Mortality, group=(Colony)))+
        ggthe_bw + ggtitle("b.") +
        geom_line(aes(colour=ITS2_14), linetype=2) +
        geom_jitter(height = 0, width = 0.25, alpha=0.4) +
        
        scale_colour_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Initial ITS2 community (August 2014)", 
                          labels=c("C1d", "C1b-c", "D.glynnii")) +
        
        scale_fill_manual(values=c("blue3","purple", "red3"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Initial ITS2 community (August 2014)", 
                          labels=c("C1d", "C1b-c", "D.glynnii")) +
        scale_shape_manual(values=c(21, 22, 24),
                      labels=c("No", "Partial", "Almost total"))+
        
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.01,0.01)) +
        
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Traject_ProportionITS2


# Figure_2_ITS2<-grid.arrange(Histo2014_DpropITS2, Traject_ProportionITS2,Histo2016_DpropITS2,
# nrow=1, widths=c(2/9, 5/9, 2/9))

# ggsave(file="Outputs/Figure_ITS2.svg", plot=Figure_2_ITS2, width=6.5, height=5)

```


```{r}

Histo2014_DpropITS2b<- Histo2014_DpropITS2 + facet_grid(ORF~.)

Histo2016_DpropITS2b<- Histo2016_DpropITS2 + facet_grid(ORF~.)

Traject_ProportionITS2b<- Traject_ProportionITS2 + facet_grid(ORF~.)

# Figure_2_ITS2b<-grid.arrange(Histo2014_DpropITS2b, Traject_ProportionITS2b,Histo2016_DpropITS2b,
# nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_2_ITS2b.svg", plot=Figure_2_ITS2b, width=7, height=4)

```


!### Figure XX: ORF

```{r}
Histo2014_DpropORF <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(ORFCommunity))) +
        ggthe_bw + coord_flip()+ ggtitle("a.")+
        geom_histogram(binwidth = 0.05, boundary=0, colour="black") +
        scale_fill_manual(values=c("gray", "white","snow", "mintcream"),
                       guide = guide_legend(title.position = "top", nrow = 2),
                      name = "")+ 
                       #labels=c("Type 3", "Type 1")) +
        scale_x_continuous(#name= expression(
                          #italic(Durusdinium)~proportion~((D/H)/(S/H))),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                          limits = c(0,16),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA),
              panel.border = element_blank(),
              axis.line = element_line(colour = "black"))
#Histo2014_DpropORF 

Histo2016_DpropORF <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(ORFCommunity))) +
        ggthe_bw + coord_flip()+ ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0, 
                       colour="black") +
        scale_fill_manual(values=c("gray", "white","snow", "mintcream"),
                       guide = guide_legend(title.position = "top", nrow = 2),
                      name = "")+ 
                       #labels=c("Type 3", "Type 1")) +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,16),
                          breaks=seq(0,15,by=5)) +
          theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA),
              panel.border = element_blank(),
              axis.line = element_line(colour = "black"))
#Histo2016_DpropORF

Traject_ProportionORF_a<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp))+
        ggthe_bw + ggtitle("b.") +
        geom_line(aes(colour=(ORF), group=(Colony)), linetype=2) +
        scale_colour_manual(values=c("black", "gray"),
                          guide = guide_legend(title.position = "top", nrow = 2),
                          name = "Pocillopora type", 
                          labels=c("Type 3", "Type 1")) +
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.01,0.01)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
  
  Traject_ProportionORF <- Traject_ProportionORF_a + 
  geom_jitter((aes(colour=factor(ORF))), 
                    height = 0, width = 0.3, color="black", size=1, shape=21) +
        scale_fill_manual(values=c("white", "gray"))
  
   #Traject_ProportionORF

# Figure_2_ORF<-grid.arrange(Histo2014_DpropORF, Traject_ProportionORF, Histo2016_DpropORF,
# nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_2_ORF.svg",plot=Figure_2_ORF, width=7, height=3.8, dpi=300)

```



!### Figure XX: ITS2 + Mortality

```{r}
data.Uva$Mor_ITS2<-paste(data.Uva$DominantITS2, data.Uva$Mortality, sep = "_")

data.Uva$Mor_ITS2<-factor(data.Uva$Mor_ITS2, levels = c(
  "C1d-dominated_No", "C1d-dominated_Partial", "C1d-dominated_Almost total",  
  "C1bc-dominated_No", "C1bc-dominated_Partial",  
  "D1-dominated_No", "D1-dominated_Partial", "D1-dominated_Almost total"))

summary(data.Uva$Mor_ITS2)

```


```{r}
Histo2014_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + coord_flip()+ ggtitle("a.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
        scale_fill_manual(values=c("skyblue1", 
                          "darkorchid1",
                          "red1"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (August 2014)") +
      
        scale_x_continuous(name= expression(
                          italic(Durusdinium)~proportion~((D/H)/(S/H))),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Histo2014_DpropITS2 

Histo2016_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + coord_flip()+ ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
       scale_fill_manual(values=c("skyblue1", "blue2", "blue4",
                          "darkorchid3",
                          "red1", "red3", "red4"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (April 2016)") +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Histo2016_DpropITS2


HistoAll_DpropITS2 <- ggplot(data.Uva, aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + coord_flip()+ ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
       scale_fill_manual(values=c("skyblue1", "blue2", "blue4",
                          "darkorchid1","darkorchid3",
                          "red1", "red3", "red4"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (April 2016)") +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA)) + facet_grid(ORF~Year)
#HistoAll_DpropITS2


Traject_ProportionITS2<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp, group=(Colony)))+
        ggthe_bw + ggtitle("b.") +
        geom_line(aes(colour=ITS2_14),linetype=2) +
        geom_jitter(aes(colour=Mor_ITS2, shape=Mortality),
                    height = 0.00, width = 0.25, alpha=0.9) +
        
        scale_colour_manual(values=c(
                          "darkorchid1", "darkorchid1","darkorchid3",
                          "skyblue1","blue4", "skyblue1", "blue2",
                          "red1", "red4", "red1", "red3" ),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (April 2016)") +
  
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.01,0.01)) +
        
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))
#Traject_ProportionITS2


# Figure_2_ITS2<-grid.arrange(Histo2014_DpropITS2, Traject_ProportionITS2,Histo2016_DpropITS2,
# nrow=1, widths=c(3/9, 3/9, 3/9))

# ggsave(file="Outputs/Figure_ITS2_Mortality.svg", plot=Figure_2_ITS2, width=7, height=4)

```


### Figure 3b and 3c: ITS2 + Mortality

```{r}
data.Uva$Mor_ITS2<-paste(data.Uva$DominantITS2, data.Uva$Mortality, sep = "_")

data.Uva$Mor_ITS2<-factor(data.Uva$Mor_ITS2, levels = c(
   "C1d-dominated_Almost total", "C1d-dominated_Partial","C1d-dominated_No",  
  "C1bc-dominated_Partial","C1bc-dominated_No",
  "D1-dominated_Almost total", "D1-dominated_Partial", "D1-dominated_No" ))

summary(data.Uva$Mor_ITS2)

```


```{r}
Histo2014_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2014), ], aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + ggtitle("a.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
        scale_fill_manual(values=c("black", 
                          "black",
                          "black"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (August 2014)") +
      
        scale_x_continuous(name= expression(
                          italic(Durusdinium)~proportion~((D/H)/(S/H))),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous((name= "Number of colonies \n (Aug 2014)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="none",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA)) + facet_grid(ORF~.)
#Histo2014_DpropITS2 

Histo2016_DpropITS2 <- ggplot(data.Uva[which(data.Uva$Year.2==2016), ], aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
       scale_fill_manual(values=c("white", "gray", "black",
                          "gray",
                          "white", "gray", "black"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (April 2016)") +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="none",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA)) +  facet_grid(ORF~.)
#Histo2016_DpropITS2


HistoAll_DpropITS2 <- ggplot(data.Uva, aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0) +
       scale_fill_manual(values=c("skyblue1", "blue2", "blue4",
                          "darkorchid1","darkorchid3",
                          "red1", "red3", "red4"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (April 2016)") +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies \n (Aug 2016)"),
                          limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA)) + facet_grid(ORF~Year)
#HistoAll_DpropITS2

HistoAll_DpropITS2 <- ggplot(data.Uva, aes (D.Prp , fill=(Mor_ITS2))) +
        ggthe_bw + ggtitle("c.")+
        geom_histogram(binwidth = 0.05, boundary=0, color = "black") +
       scale_fill_manual(values=c("white", "gray", "black",
                          "gray","black",
                          "white", "gray", "black"),
                          guide = guide_legend(title.position = "top", nrow = 3),
                          name = "Dominant ITS2 community (April 2016)") +
        scale_x_continuous(name="",
                           breaks=(seq(0,1,by=0.1)),
                           expand=c(0.01,0.01)) +    
        scale_y_continuous((name= "Number of colonies"),
                          limits = c(0,14),
                          breaks=seq(0,14,by=2)) +
        theme(legend.position="bottom",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA)) + 
        facet_grid(ORF~Year) + theme(legend.position = "none")
#HistoAll_DpropITS2
#ggsave(file="Outputs/Panels.svg", plot=HistoAll_DpropITS2, width=6, height=2.8)



Traject_ProportionITS2<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp, group=(Colony)))+
        ggthe_bw + ggtitle("b.") +
        geom_line(linetype=2) +
        geom_jitter(aes(colour=Mortality, shape=ORF), size=1.5,
                    height = 0.00, width = 0.25, alpha=1) +
        
        scale_colour_manual(values=c("black", "gray","white")) +
  
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.02,0.02)) +
        
        theme(legend.position="none",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))# + facet_grid(ORF~.)
#Traject_ProportionITS2
#ggsave(file="Outputs/Trajectory.svg", plot=Traject_ProportionITS2, width=6.5, height=3)

# Figure_2_ITS2<-grid.arrange(Histo2014_DpropITS2, Traject_ProportionITS2,Histo2016_DpropITS2,
# nrow=1, widths=c(2.5/9, 4/9, 2.5/9))

# ggsave(file="Outputs/Figure_ITS2_Mortality2.svg", plot=Figure_2_ITS2, width=7, height=4)

```

```{r}
DpropORF <- ggplot(data.Uva, aes (D.Prp , fill=(Mortality))) +
        ggthe_bw + ggtitle("c.")+
        geom_histogram(binwidth = 0.1, boundary=0, color="black") +
        scale_fill_manual(values=c("black", 
                          "gray",
                          "white"),
                          guide = guide_legend(title.position = "top", nrow = 1),
                          name = "Colony condition") +
      
        scale_x_continuous(name= expression(
                          italic(Durusdinium)~proportion~((D/H)/(S/H))),
                          breaks=(seq(0,1,by=0.1)),
                          expand=c(0.01,0.01)) +
        scale_y_continuous(limits = c(0,17),
                          breaks=seq(0,15,by=5)) +
        theme(legend.position="top",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA)) + facet_grid(ORF~Year)
#DpropORF 

Traject_ORF<- ggplot(data.Uva, aes (x=Year.2, y=D.Prp, group=(Colony)))+
        ggthe_bw + ggtitle("b.") +
        geom_line(linetype=2) +
        geom_jitter(aes(colour=Mortality, shape=ORF), size=2,
                    height = 0.00, width = 0.25, alpha=1) +
        
        scale_colour_manual(values=c("black", "gray","white")) +
  
        scale_x_continuous(name="", 
                           breaks = c(2014, 2015, 2016),
                           labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016")) +
        scale_y_continuous((name= ""),
                           breaks=seq(0,1,by=0.1),
                           expand=c(0.02,0.02)) +
        
        theme(legend.position="none",
              legend.title.align=0.5,
              strip.background =element_rect(fill=NA))# + facet_grid(ORF~.)
#Traject_ORF

Figure_3bc_ORF<-grid.arrange(Traject_ORF, DpropORF,
nrow=2, heights=c(1.2/3, 1.8/3))

#ggsave(file="Outputs/Fig3_v8.svg", plot=Figure_3bc_ORF, width=6.5, height=7)

```


```{r}
# Summary dominant genera
  Community_prescence_absence<-data.Uva %>%
        group_by(ORF, Community, Year.2) %>%
        dplyr::summarise(total.count=n()) 
  Community_prescence_absence
  
  Community_dominance<-data.Uva %>%
        group_by(ORF, DominantCommunity, Year.2) %>%
        dplyr::summarise(total.count=n()) 
  Community_dominance
  
  Community_dominance<-data.Uva %>%
        group_by(ORF, Year.2, DominantCommunity,
                Community) %>%
        dplyr::summarise(total.count=n()) 
  Community_dominance
  
  # SH_mean<-data.Uva %>%
  #       group_by(ORF, Year.2, DominantCommunity) %>%
  #       dplyr::summarise(mean=mean(tot.SH)) 
  # SH_mean
  # 
  # SH_SE<-data.Uva %>%
  #       group_by(ORF, Year.2, DominantCommunity) %>%
  #       dplyr::summarise(sd=sd(tot.SH)) 
  # SH_SE
``` 

## 7b. Changes in total Symbiodiniaceae abundance (bleaching): qPCR + ORF

### Figure 3: ORF + Dominant symbiont

```{r}
#SH_2014CoI<-lm(logTot.SH ~ Year * ORF * DominantCommunity,             data=data.Uva)
SH_2014CoI<-lmerTest::lmer(logTot.SH ~ Year * ORF * DominantCommunity + (1|Colony), data=data.Uva)

    summary(SH_2014CoI)
    anova(SH_2014CoI)
    ranova(SH_2014CoI)
    step(SH_2014CoI, reduce.random=FALSE)
    
    SH_2014CoI<-lm(logTot.SH ~ Year * ORF * DominantCommunity, data=data.Uva)
    
    SH_I.emmc<-emmeans(SH_2014CoI, ~Year*ORF*DominantCommunity)
    SH_I_groups<-multcomp::cld(SH_I.emmc)
    SH_I_groups<-as.data.frame(SH_I_groups[complete.cases(SH_I_groups),])
    SH_I_groups<-SH_I_groups[order(
      SH_I_groups$Year, SH_I_groups$ORF),]
    SH_I_groups
    
    #write.csv(SH_I_groups,"Outputs/SH_ORF_Dominant_groups2.csv")
    
# plot(emmeans(SH_2014CoI, ~Year|~DominantCommunity), comparisons = TRUE) + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE) + facet_wrap(~DominantITS2)+ ggthe_bw
    
```   

```   {r}
    
SH_2014ComI <- ggplot(data.Uva, aes (Year.2, logTot.SH, colour=factor(DominantITS2))) +  ggthe_bw + facet_wrap(~ORF) + ggtitle("a.")+
  #geom_point(alpha=0.5)+
  #geom_line(aes(group=(Colony)))+
  stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2,
                   position=position_dodge(width=0.5))+
  stat_summary(fun.data = "mean_cl_boot",geom = "point", 
                   position=position_dodge(width=0.5))+
  stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.5)) +
   scale_colour_manual(values=c("blue3","blue3" , "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Dominant symbiont",
                        labels=c("Cladocopium", "Durusdinium"))+
      theme(legend.position="mone",
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-3, -0.1),
            name="\n Total symbiont to host cell ratio (S/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" ", "", " ")) 
SH_2014ComI


#ggsave(file="Figure_3.svg", plot=SH_ITS2_Comunities, width=6, height=4, dpi=300)

```   


## 8b. Changes in *Cladocopium* abundance

```{r LmerC_ITS2}

CH_Com2ITS2 <- ggplot(data.Uva, aes (Year.2, logC.SH, colour=factor(D14Dominant))) + ggthe_bw+ ggtitle("c.") + facet_grid(~ORF) + 
  geom_point(alpha=0.5)+
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3))+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue3", "red3"),
                         guide = guide_legend(title.position = "top", nrow = 3),
                         name = "Dominant symbiont",
                         labels=c("Cladocopium", "Durusdinium"))+
     theme(legend.position="mone",
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-6, -0.1),
            name="\n Cladocopium to host cell ratio (C/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                         labels = c(" ", " ", " ")) 
CH_Com2ITS2


CH_I<-lmerTest::lmer(logC.SH ~ Year* DominantITS2 + (1|Colony), data=data.Uva)
    summary(CH_I)
    anova (CH_I)
    #step(CH_I)

    CH_I.emmc<-emmeans(CH_I, ~Year*DominantITS2)
    CH_I_groups<-cld(CH_I.emmc)
    CH_I_groups<-as.data.frame(CH_I_groups[complete.cases(CH_I_groups),])
    CH_I_groups<-CH_I_groups[order(CH_I_groups$DominantITS2,CH_I_groups$Year),]
    CH_I_groups
    #write.csv(CH_I_groups,"CH_I_groups.csv")
    ```
   
## 9b. Changes in *Durusdinium* abundance

```{r LmerD_ITS2}

DH_Com2ITS2 <- ggplot(data.Uva, aes (Year.2, logD.SH, colour=factor(D14Dominant))) +  # geom_point(alpha=0.5)+
      ggthe_bw+ ggtitle("d.")+ facet_grid(~ORF) +
    
      stat_summary(fun.data = "mean_cl_boot",geom = "errorbar", width = 0.2, position=position_dodge(width=0.3))+
      stat_summary(fun.data = "mean_cl_boot",geom = "point", position=position_dodge(width=0.3))+
      stat_summary(fun.y=mean, geom="line", position=position_dodge(width=0.3)) +
      
      scale_colour_manual(values=c("blue", "red3"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Dominant symbionts",
                        labels=c("Cladocopium-dominated", "Durusdinium-dominated"))+
      theme(legend.position=c(0.75,0.5),
            legend.box.background = element_rect(),
            strip.background =element_rect(fill="white"))+
   
      scale_y_continuous(limits = c(-6, -0.1),
            name="\n Durusdinium to host cell ratio (D/H)", 
            labels = (math_format(10^.x)),
            expand = c(0.0, 0)) + 
      scale_x_continuous(name="", 
                         breaks = c(2014, 2015, 2016),
                        # labels = c(" Aug \n 2014", " Aug \n 2015", " Apr \n 2016"))
                        labels = c(" ", " ", " "))

DH_Com2ITS2

DH_LM_ITS2<-lmer(logD.SH ~ Year* DominantITS2 + (1|Colony), data=data.Uva)
    summary(DH_LM_ITS2)
    #step(DH_LM_ITS2)

    DH_I.emmc<-emmeans(DH_LM_ITS2, ~Year*DominantITS2)
    DH_groups_I<-cld(DH_I.emmc)
    DH_groups_I<-as.data.frame(DH_groups_I[complete.cases(DH_groups_I),])
    DH_groups_I<-DH_groups_I[order(DH_groups_I$DominantITS2,DH_groups_I$Year),]
    DH_groups_I
    #write.csv(DH_groups_I,"Output/DH_I_groups.csv")
    ```

### Figure 4: qPCR by Pocillopora lineage

```{r}
Figure_4<-grid.arrange(SH_2014ComI, CH_Com2ITS2, DH_Com2ITS2,nrow=3)

Figure_4_InitailCommunity<-grid.arrange(CH_Com2ITS2, DH_Com2ITS2,nrow=2)

# ggsave(file="Outputs/Figure_3c.svg", plot=Figure_3, width=7, height=11)

# ggsave(file="Outputs/Figure_3d.png", plot=Figure_3_InitailCommunity, width=7, height=7)


```
---

## 10. Supplementary C/H D/H dynamics

Select data

```{r}
log_Log.data<-data.Uva[,c("Colony","Year.2", "C.SH", "D.SH", 
                          "D14Community", "Community","ITS2_14",
                          "ORF", "DominantITS2", "Mortality", "Mor_ITS2")]

log_Log.data<-log_Log.data %>%
  filter(Year.2 != "2015")

log_Log.data$Yr<-as.factor(log_Log.data$Year.2)
log_Log.data$Yr_M<-as.factor(
                            paste(log_Log.data$Yr,
                                  log_Log.data$Mortality,
                                  sep = "_"))

log_Log.data$logC<-log10(log_Log.data$C.SH)
log_Log.data$logD<-log10(log_Log.data$D.SH)
log_Log.data$logC[which(log_Log.data$C.SH==0)] <- -6
log_Log.data$logD[which(log_Log.data$D.SH==0)] <- -6

```

* ITS2-ORF

```{r}

Community_Changes1 <- ggplot (log_Log.data, aes(logC, logD, group=Colony, colour=ITS2_14, shape=ORF)) +

  geom_abline(intercept=0, slope=1, linetype=1, color="black")+
  geom_abline(intercept=-1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=-2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=-3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-5, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=5, slope=1, linetype=2, color="gray")+
  scale_colour_manual(values=c("blue","purple", "red"),
                        guide = guide_legend(title.position = "top", nrow = 3),
                        name = "Dominant ITS2 types (2014)",
                        labels=c("C1d", "C1b-c", "D1"))+
  
  ggthe_bw + theme(legend.position="bottom", 
                    legend.box = "horizontal")+
  scale_x_continuous(limits = c(-6,-0.1), "log10 (C/H cell ratio)")+
  scale_y_continuous(limits = c(-6,-0.1), "log10 (D/H cell ratio)") +
  
  geom_point(alpha=0.5, size=4) +
  geom_path(size = 1,arrow =
              arrow(type = "open", angle = 30, length = unit(0.1, "inches")))+
  
 annotate("text", x = c(seq(-5.1, -1.1, by=1)), y = -0.9, label = c(
    "10,0000D : 1C", "1,000D : 1C", "100D : 1C","10D : 1C", "C : D"), angle = 45)+
  annotate("text", x = -0.9, y = c(seq(-4.7, -1.7, by=1)), label = c(
    "1D : 10,000C", "1D : 1,000C", "1D : 100C",  "1D : 10C"), angle = 45)
  
Community_Changes1

#ggsave(file="FigAndrewsFavoriteGraph_ITS2.png", plot=Community_Changes1, width=5.5, height=7.1)
``` 

* ITS2-Mortality 

```{r}
Community_Changes2 <- ggplot (log_Log.data, aes(logC, logD, group=Colony, colour=ITS2_14)) +

  geom_abline(intercept=0, slope=1, linetype=1, color="black")+
  geom_abline(intercept=-1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=-2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=-3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-5, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=5, slope=1, linetype=2, color="gray")+
  scale_colour_manual(values=c("blue","purple", "red"),
        guide = guide_legend(title.position = "top", nrow = 3),
                         name = "Initial ITS2",
                        labels=c("Cd1", "C1b-c", "D1"))+
  #scale_colour_manual(values=c("skyblue1", "blue2", "blue4",
  #                        "darkorchid1","darkorchid3",
  #                        "red1", "red3", "red4"))+
  
  ggthe_bw + 
  theme(legend.position="bottom", 
                   legend.box = "vertical")+
  #theme(legend.position="none")+
  
  scale_x_continuous(limits = c(-6,-0.1), 
                     "Cladocopium abundance (log10 C/H))")+
  scale_y_continuous(limits = c(-6,-0.1), 
                     "Durusdinium abundance (log10 D/H))") +
  geom_point(aes(shape=Mortality),
             alpha=0.5, size=3) +
  geom_path(size = 0.5 , arrow =
             arrow(type = "open", angle = 30,
                  length = unit(0.1, "inches")))+
  
 annotate("text", x = c(seq(-5.1, -1.1, by=1)), y = -0.9, label = c(
    "10,0000D : 1C", "1,000D : 1C", "100D : 1C","10D : 1C", "C : D"), angle = 45)+
  annotate("text", x = -0.9, y = c(seq(-4.7, -1.7, by=1)), label = c(
    "1D : 10,000C", "1D : 1,000C", "1D : 100C",  "1D : 10C"), angle = 45)
  
Community_Changes2


#ggsave(file="LogLog_labels.svg", plot=Community_Changes2, width=5.5, height=6)

```

* Colony 

```{r}
Community_Changes3 <- ggplot (log_Log.data, aes(logC, logD, group=Colony, colour=Colony)) +

  geom_abline(intercept=0, slope=1, linetype=1, color="black")+
  geom_abline(intercept=-1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=-2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=-3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=-5, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=1, slope=1, linetype=2, color="black")+
  geom_abline(intercept=2, slope=1, linetype=2, color="darkgray")+
  geom_abline(intercept=3, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=4, slope=1, linetype=2, color="gray")+
  geom_abline(intercept=5, slope=1, linetype=2, color="gray")+
  #scale_colour_manual(values=c("blue","purple", "red"),
   #                     guide = guide_legend(title.position = "top", nrow = 3),
    #                    name = "Detected symbionts (2014)",
     #                   labels=c("Cladocopium", "Mixed", "Durusdinium"))+
  
  ggthe_bw + theme(legend.position="none")+
  scale_x_continuous(limits = c(-6,-0.1), "log10 (C/H cell ratio)")+
  scale_y_continuous(limits = c(-6,-0.1), "log10 (D/H cell ratio)") +
  
  geom_point(aes(shape=Yr), alpha=0.5, size=4) +
  geom_path(size = 1,arrow =
              arrow(type = "open", angle = 30, length = unit(0.1, "inches")))+
  
  annotate("text", x = c(seq(-5.1, -1.1, by=1)), y = -0.9, label = c(
    "10,0000D : 1C", "1,000D : 1C", "100D : 1C","10D : 1C", "C : D"), angle = 45)+
  annotate("text", x = -0.9, y = c(seq(-4.7, -1.7, by=1)), label = c(
    "1D : 10,000C", "1D : 1,000C", "1D : 100C",  "1D : 10C"), angle = 45)
  
Community_Changes3

# ggsave(file="LogLog_Colony.svg", plot=Community_Changes3, width=6, height=6)

```

## 5c. Changes in the number of colonies dominated by each genus considering mortality

* Fisher test including initially (Aug 2014) 50/50 colonies. Both colonies were placed in the D-dominated category to be conservative.

```{r}
# Only type 1 colonies (n=23)

Input =("
Year    C     D
2014    9    14
2016    2    18
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")


# Type 1 and type 3 colonies

Input =("
Year    C     D
2014    15    14
2016    4     18
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")



# Spp changes

Input =("
Year    I     II
2014    23    6
2016    20    2
")

Matriz <- as.matrix(read.table(textConnection(Input),
                               header=TRUE, 
                               row.names=1))
fisher.test(Matriz,
            alternative="two.sided")

```


